A thesis draft

### 2018-09-20 draft.tex
Complete docker-compose paragraph

The analysis of this topic revealed to be trivial: since internet has many 
different protocols that would become infeasible to support all of them at the 
same time, packet incapsulation revealed to be the solution: every packet 
incoming in the VNFs have been previously incapsulated by the MANO, making the 
whole architecture indipendent from the protocol a particolar data-flux uses. 
To achieve this, TUN/TAP\todo{Find out acronym} interfaces were used to deploy 
a tunnel between VNFs, allowing them to pass packets encapsulated in UDP ones.

@@

As already introduced before, Kubernetes is an open source software framework 
specialized in container management and orchestration. Developed by Google in 
??\todo{Find out the actual date} and written in Go, it allows different 
machines (called nodes from now on) to create an abstraction layer and to form 
a cluster where is possible to run Docker containers without brothering about 
hardware constraints. Nodes can have specific roles and specialization, all of 
them managed by one or many master nodes, that actually manage the 
orchestration.
On top of that, Kubernetes is virtualization-agnostic, meaning that it offers 
the possibility to change the virtualization software in use (i.e. from 
Container-based technology to Virtual machine software).

@@

In recent years, with the new hardware capabilities and the recent development 
of in-kernel virtualization systems (such as Hyper-V) this technology 
begin to be adopted. Virtualization allows to run different systems on the 
same machine, making them completely isolated and then more resilient to 
failures. The back of the medal, though, is that virtual machines require large 
amount of resources, especially memory, because solutions like copy-and-write 
of in-memory pages are not viable anymore (since the kernel gets duplicated 
too), leading to duplication of loaded libraries and assets in the memory of 
the host. 
For large deployment containing only simple services (e.g. a backend 
application serving a website or a database) this ends up in a waste of 
resources. \todo{Talk about lxc containers and how Docker solved magically the 
problem.} It's here that, in ??\todo{Find Docker date of birth}, Docker was 
created, basing its solution on an already existing product: Linux Container 
(LXC). From this framework, Docker built an entire ecosystem, consisting in a 
client/server model giving the possibility for users to simply launch, scale and 
delete containers (locally or remotely with Docker-machine), a repository 
system where images, a layer-based ``core'' where containers start running from 
when they are launched, can be stored and tagged in a sort of version control 
system. Finally, another couple of solutions, called Docker-compose, and Docker 
Swarm have the purpose to, respectively, orchestrate containers in a single or 
a clustered system.

\paragraph{Docker Swarm} Introduced in ??\todo{Find Docker Swarm date of
birth}, Docker Swarm allows multiple Docker nodes to cluster together and be
seen as one logical unit. This layer completely makes the underlying
infrastructure transparent: data management, as network one, are totaly managed
by Docker. Recently, Docker-compose support has been introduced, making
this one-node tool available for clustered systems. At the end of the day, on
one hand Docker Swarm provides an easy way to set up a cluster system with all
the tools configured out-of-the-box, without the necessity to set networking
configurations or installing ad-hoc storage solutions. On the other hand,
though, it doesn't have all the personalization options that Kuberentes offers,
thus making the product less flexible. This foundamental characteristic,
although, makes the two solutions have different use cases leading to different
market needs.

\paragraph{Docker-compose} As briefly discussed above, Docker-compose is a tool 
that allows services orchestration. It automates most of the tasks that should 
be performed by hand when launching one or multiple docker containers. It's 
particulary useful when more continers have to \textbf{INTERAGIRE}\todo{Find 
translation} between them, because\todo{Write down docker-commpose 
functionalities and describe the product a little bit}

@@

Starting with the first step of creating a MANO able to process incoming data 
packets through VNF functions, we encountered that many networking tools 
already 
present in the market required some tweaking and some integrations, shifting 
our 
goal to create a complete  European Telecommunications Standards Institutes 
(ETSI) Management and orchestrator (MANO) testbed instead, following the 
specifications suggested in the RFC 7665, thus implementing only the first 
three 
requisites, without digging in the satellite data flow optimization.

>>>>

The analysis of this topic revealed to be trivial: since internet has many
different protocols that would become infeasible to support all of them at the
same time, packet incapsulation present itself as the only faseable solution:
every packet incoming in the VNFs has already been incapsulated by the MANO,
\todo{Not sure about this, please give it a check} making the whole
architecture indipendent from the protocol a particolar flux of data uses. To
achieve this, TUN/TAP\todo{Find out acronym} interfaces were used to deploy a
tunnel between VNFs, allowing them to pass packets encapsulated in UDP ones.

@@

As already introduced before, Kubernetes is an open source software framework
specialized in container management and orchestration. Developed by Google in
??\todo{Find out the actual date} and written in Go, it allows different
machines (called nodes from now on) to create an abstraction layer and to form
a cluster where is possible to run Docker containers without brothering about
hardware constraints. Nodes can have specific roles and specialization, all of
them managed by one or many master nodes, that actually manage the
orchestration.
On top of that, Kubernetes is virtualization-agnostic, meaning that it offers
the possibility to change the virtualization software in use (i.e. from
Container-based technology to Virtual machine software).\todo{Add Kubernetes
logo}

@@

In recent years, with the new hardware capabilities and the recent development
of in-kernel virtualization systems (such as Hyper-V) this technology
begin to be adopted. Virtualization allows to run different systems on the
same machine, making them completely isolated and then more resilient to
failures. The back of the medal, though, is that virtual machines require large
amount of resources, especially memory, because solutions like copy-and-write
of in-memory pages are not viable anymore (since the kernel gets duplicated
too), leading to duplication of loaded libraries and assets in the memory of
the host.
For large deployment containing only simple services (e.g. a backend
application serving a website or a database) this ends up in a waste of
resources. \todo{Talk about lxc containers and how Docker solved magically the
problem.} It's here that, in ??\todo{Find Docker date of birth}, Docker was
created, basing its solution on an already existing product: Linux Container
(LXC). From this framework, Docker built an entire ecosystem, consisting in a
client/server model giving the possibility for users to simply launch, scale and
delete containers (locally or remotely with Docker-machine), a repository
system where images, a layer-based ``core'' where containers start running from
when they are launched, can be stored and tagged in a sort of version control
system. Finally, another couple of solutions, called Docker-compose, and Docker
Swarm have the purpose to, respectively, orchestrate containers in a single or
a clustered system. \todo{Add Docker, docker-machine logos}

\paragraph{Docker Swarm} Introduced in ??\todo{Find Docker Swarm date of
birth}, Docker Swarm allows multiple Docker nodes to cluster together and be
seen as one logical unit. This layer completely makes the underlying
infrastructure transparent: data management, as network one, are totaly managed
by Docker. Recently, Docker-compose support has been introduced, making
this one-node tool available for clustered systems. At the end of the day, on
one hand Docker Swarm provides an easy way to set up a cluster system with all
the tools configured out-of-the-box, without the necessity to set networking
configurations or installing ad-hoc storage solutions. On the other hand,
though, it doesn't have all the personalization options that Kuberentes offers,
thus making the product less flexible. This foundamental characteristic,
although, makes the two solutions have different use cases leading to different
market needs. \todo{Add Docker Swarm}

\paragraph{Docker-compose} As briefly discussed above, Docker-compose is a tool
that allows services orchestration. It automates most of the tasks that should
be performed by hand when launching one or multiple docker containers. It's
particulary useful when more continers have to interact together,
because\todo{Write down docker-commpose functionalities and describe the product
a little bit} all the services rules are described in a simple YAML file.
With the birth of Docker Swarm, work has started to port this tool to the Swarm
framework. At the time of this writing, the procedure to port a Docker-compose
configuration in Docker Swarm is still not completely transparent, and it
requires a sort of compilation, where Docker-compose bundles all the
necessaries resources into a binary file that Docker Swarm will use to allocate
the necessary resources.

@@

Starting with the first step of creating a MANO able to process incoming data
packets through VNF functions, we encountered that many networking tools
already present in the market required some tweaking and some integrations,
shifting our goal to create a complete  European Telecommunications Standards
Institutes (ETSI) Management and orchestrator (MANO) testbed instead, following
the specifications suggested in the RFC 7665, thus implementing only the first
three requisites, without digging in the satellite data flow optimization.
\todo{This section needs to be expanded a lot!!!}
